% ============================================
% PROJECTS
% ============================================

\section{Projects}

\textbf{TEKNOFEST – Autonomous Underwater Vehicle (AUV) | Software \& Simulation} \hfill \textit{Python, ROS 2, Gazebo, Pixhawk} \\
\vspace{0pt}
\begin{itemize}
    \item Conducted R\&D studies on the design and simulation of an autonomous underwater vehicle within the scope of TEKNOFEST.
    \item Performed modeling of vehicle dynamics and control algorithms in \textbf{ROS 2} and \textbf{Gazebo} environments.
    \item Worked on \textbf{Sensor Fusion} architecture including IMU, pressure, and sonar sensor data for state estimation.
    \item Tested basic motion and depth control scenarios in simulation using \textbf{Python}-based modules.
\end{itemize}

\vspace{6pt}

\noindent \textbf{Digital Dental World Platform (Active Development Phase) | Full Stack Developer} \hfill \textit{Vue.js, Laravel, MySQL} \\
\vspace{0pt}
\begin{itemize}
    \item Developing a modern and scalable platform bringing dentists, laboratories, and sector companies together in a single ecosystem.
    \item Designing an end-to-end web application focusing on user experience, interactive interfaces, and sector-specific needs.
    \item Using \textbf{Vue.js} on the frontend, \textbf{Laravel} on the backend, and \textbf{MySQL} as the database.
\end{itemize}

\vspace{6pt}

\noindent \textbf{Automated LaTeX CV Template | Design \& Automation} \hfill \textit{LaTeX, Docker, CI/CD} \\
\vspace{0pt}
\begin{itemize}
    \item Designed and developed a customizable \textbf{LaTeX} template for a professional and modern look.
    \item Integrated \textbf{Docker} containerization to ensure build environment independence and consistency.
    \item Improved maintainability and updateability by organizing source code in a modular structure (sections).
\end{itemize}
